Network segregation, Social Isolation and Preference for Redistribution across societies

### 2023-09-19 paper.Rmd
Update paper.Rmd

@@

```{r,results='asis', cache=T}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass,
                        incomepcap,
                        gini_disp,
                        gini_mkt,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,pi_isola,
                        # union,
                        # labst,
                        # WEIGHT
                        ) %>% 
  mutate(logrgdpna=log(rgdpna)) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>% 
  na.omit()

# lineal
base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
homclass <- lmer(redist~1 + female+agenum + homclass +(1|country2),data=dfreg)
class <- lmer(redist~1 +female+agenum + class3+(1|country2),data=dfreg)
full <- lmer(redist~1 +female+agenum + class3 +edyears+homclass+incomepcap+(1|country2),data=dfreg)
# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + edyears + incomepcap + homclass*class3 +(1|country2),data=dfreg)
models <- list(homclass,class,full,full_int1)

cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
omitcoef <- "(Intercept)|(agenum)|(female)|(incomepcap)|(edyears)|(logrgdpna)"
coefname <- c("Network class homogeneity","Service Class","Working Class",
              "Homogeneity x Service Class","Homogeneity x Working Class")
coefgroup <- list("Social Class (ref: Intermediate class)"=2:3,"Interaction:"=4:5)
gofrow <-  list(Controls=c("Yes","Yes","Yes","Yes"))
gof1<-  c(NA,NA,"Num. countries:","Var: Group",NA)

>>>>

- controls educ and income
- laborstatus

@@

```{r,results='asis', cache=T}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass,
                        Q05pcm,
                        gini_disp,
                        gini_mkt,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,pi_isola,
                        union,
                        labst,
                        # WEIGHT
                        ) %>% 
  mutate(logrgdpna=log(rgdpna)) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>% 
  na.omit()

# lineal
base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
homclass <- lmer(redist~1 + female+agenum + homclass +(1|country2),data=dfreg)
class <- lmer(redist~1 +female+agenum + class3+(1|country2),data=dfreg)
full <- lmer(redist~1 +female+agenum + class3 +edyears+homclass+Q05pcm+(1|country2),data=dfreg)
# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + edyears + Q05pcm + homclass*class3 +(1|country2),data=dfreg)
models <- list(homclass,class,full,full_int1)

cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
omitcoef <- "(Intercept)|(agenum)|(female)|(Q05pcm)|(edyears)|(logrgdpna)"
coefname <- c("Network class homogeneity","Service Class","Working Class",
              "Homogeneity x Service Class","Homogeneity x Working Class")
coefgroup <- list("Social Class (ref: Intermediate class)"=2:3,"Interaction:"=4:5)
gofrow <-  list(Controls=c("Yes","Yes","Yes","Yes"))
gof1<-  c(NA,NA,"Num. countries:","Var: Group",NA)
